Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}

### 2023-03-05 tex/m2ef/daluiso_nastasi_pallavicini_polo_rl_for_options_on_tvf.tex
Update section 3.2

\usepackage[normalem]{ulem}
\newcommand\soutpars[1]{\let\helpcmd\sout\parhelp#1\par\relax\relax}
\long\def\parhelp#1\par#2\relax{%
  \helpcmd{#1}\ifx\relax#2\else\par\parhelp#2\relax\fi%
}
\newcommand{\change}[1]{{\color{red} {#1}}}%{{#1}}
\newcommand{\remove}[1]{{\color{red} \soutpars{{#1}}}}%{}
\newcommand{\removeeq}[1]{{\color{red} \sout{{#1}}}}%{}
\newcommand{\changeB}[1]{{\color{blue} {#1}}}%{{#1}}
\newcommand{\removeB}[1]{{\color{blue} \soutpars{{#1}}}}%{}
\newcommand\hcancel[2][red]{\setbox0=\hbox{$#2$}%
\rlap{\raisebox{.45\ht0}{\textcolor{#1}{\rule{\wd0}{1pt}}}}#2}

@@

\institute{Financial Engineering, Intesa Sanpaolo Group,\\
Largo Mattioli 3, 20121 Milan, Italy\\
\email{\{Roberto.Daluiso, Andrea.Pallavicini\}@intesasanpaolo.com} \and
Financial Engineering, Marketz S.p.A.,\\
Corso Europa, 2, 20122 Milan, Italy\\
\email{Emanuele.Nastasi@marketz.eu} \and \change{Financial Risk Methodologies, Unicredit S.p.A.,\\ Piazza Gae Aulenti, 3, 20154 Milan, Italy \\ \email{Stefano.Polo@unicredit.eu}}
}

@@

\subsection{Stochastic \change{o}ptimal \change{c}ontrol \change{p}roblem}
In presence of valuation adjustments, we need to solve the full optimization problem. We discretize the optimal strategy $\alpha_t$ as\footnote{We use the symbol $\mathbf{1}_A$ for the indicator function of a subset $A$.}
\begin{equation}
    \alpha_t \coloneqq \sum_k \mathbf{1}_{ \{t \in [T_{k-1}, T_k)\}}\alpha_{T_{k-1}} \; ,
\label{eq:piecewise_strategy}\end{equation}
according to a time grid $\mathcal{T}\coloneqq \{T_0,...,T_k,...,T_m\}$ with $T_0\coloneqq t$ the pricing date and $T_m \coloneqq T$ the maturity of the option. 
Therefore we can apply the dynamic programming principle to express the optimal $\alpha_t$ at time $T_{k-1}$ as
\begin{equation}
    \alpha_{T_{k-1}}\coloneqq \argmax_{\alpha} \left\{\mathbb{E}_{T_{k-1}}\left[D\left(T_{k-1},T_{k} \right) V_{T_{k}}\left(X_{T_{k}}, I_{T_{k}}(\alpha)\right) \mid X_{T_{k-1}}, I_{T_{k-1}}\right]\right\} \; ,
\label{eq:recursion}\end{equation}
where $V_{T_k}$ is the option value at time $T_k$ and $X$ is any Markovian state such that the drift and the diffusion coefficient of $I_t$ are a function of $\left(X_t,I_t,\alpha_t\right)$. We calculate $I_{T_k}\left(\alpha_{T_{k-1}}\right)$ for any given strategy $\alpha_{T_{k-1}}$ by a suitable discretization of \eqref{eq:TVS_last} starting from $X_{T_{k-1}}$ and $I_{T_{k-1}}$.

Thus the derivative price is given by:
\begin{equation}
\begin{aligned}
	    V_{T_{k-1}}\left(X_{T_{k-1}}, I_{T_{k-1}}\right)= \\ 
	     \mathbb{E}_{T_{k-1}}\left[D\left(T_{k-1},T_{k}\right) V_{T_{k}}\left(X_{T_{k}}, I_{T_{k}}\left(\alpha_{T_{k-1}}\right)\right) \mid X_{T_{k-1}}, I_{T_{k-1}}\right] \; ,
\end{aligned}
\label{eq:recursion2}\end{equation}
while the iteration starts from maturity date where the boundary condition is set equal to the payoff function:
\begin{equation}
    V_{T_m} = \Phi\left(I_{T_m}\right) \; .
\end{equation}

>>>>

\usepackage[normalem]{ulem}
\newcommand\soutpars[1]{\let\helpcmd\sout\parhelp#1\par\relax\relax}
\long\def\parhelp#1\par#2\relax{%
  \helpcmd{#1}\ifx\relax#2\else\par\parhelp#2\relax\fi%
}
\newcommand{\change}[1]{{\color{red} {#1}}}%{{#1}}
\newcommand{\remove}[1]{{\color{red} \soutpars{{#1}}}}%{}
\newcommand{\removeeq}[1]{{\color{red} \sout{{#1}}}}%{}
\newcommand{\changeB}[1]{{\color{blue} {#1}}}%{{#1}}
\newcommand{\removeB}[1]{{\color{blue} \soutpars{{#1}}}}%{}
\newcommand{\changeE}[1]{{\color{purple} {#1}}}%{{#1}}
\newcommand{\removeE}[1]{{\color{purple} \soutpars{{#1}}}}%{}
\newcommand\hcancel[2][red]{\setbox0=\hbox{$#2$}%
\rlap{\raisebox{.45\ht0}{\textcolor{#1}{\rule{\wd0}{1pt}}}}#2}

@@

\institute{Financial Engineering, Intesa Sanpaolo Group,\\
Largo Mattioli 3, 20121 Milan, Italy\\
\email{\{Roberto.Daluiso, Andrea.Pallavicini\}@intesasanpaolo.com} \and
\changeE{Digital Development Sales \& Trading Milan, Unicredit Bank AG Milano,}\\
\changeE{Piazza Gae Aulenti, 4, 20154 Milan, Italy}\\
\email{\changeE{Emanuele.Nastasi@unicredit.eu}} \and \change{Financial Risk Methodologies, Unicredit S.p.A.,\\ Piazza Gae Aulenti, 3, 20154 Milan, Italy \\ \email{Stefano.Polo@unicredit.eu}}
}

@@

\subsection{Stochastic \change{o}ptimal \change{c}ontrol \change{p}roblem}
In presence of valuation adjustments, we need to solve the full optimization problem. We discretize the optimal strategy $\alpha_t$ as\footnote{We use the symbol $\mathbf{1}_A$ for the indicator function of a subset $A$.}
\begin{equation}
    \alpha_t \coloneqq \sum_k \mathbf{1}_{ \{t \in [T_{k-1}, T_k)\}}\alpha_{T_{k-1}} \; ,
\label{eq:piecewise_strategy}\end{equation}
according to a time grid $\mathcal{T}\coloneqq \{T_0,...,T_k,...,T_m\}$ with $T_0\coloneqq t$ the pricing date and $T_m \coloneqq T$ the maturity of the option. 
Therefore we can apply the dynamic programming principle to express the optimal $\alpha_t$ at time $T_{k-1}$ as
\begin{equation}
    \alpha_{T_{k-1}}\coloneqq \argmax_{\alpha} \left\{\mathbb{E}_{T_{k-1}}\left[D\left(T_{k-1},T_{k} \right) V_{T_{k}}\left(X_{T_{k}}, I_{T_{k}}(\alpha)\right) \mid X_{T_{k-1}}, I_{T_{k-1}}\right]\right\} \; ,
\label{eq:recursion}\end{equation}
where $V_{T_k}$ is the option value at time $T_k$ and $X$ is any Markovian state such that the drift and the diffusion coefficient of $I_t$ are a function of $\left(X_t,I_t,\alpha_t\right)$ \changeE{and we indicated with $I_{T_k}\left(\alpha\right)$ the value of the strategy on the point $T_{k}$ for a given choice of the weights $\alpha$ at the previous step on the time grid.} We calculate \changeE{the strategy value for the optimal weights $\alpha_{T_{k-1}}$, namely} $I_{T_k}\left(\alpha_{T_{k-1}}\right)$ \removeE{for any given strategy $\alpha_{T_{k-1}}$} by a suitable discretization of \eqref{eq:TVS_last} starting from $X_{T_{k-1}}$ and $I_{T_{k-1}}$\removeE{.} \changeE{and}
\removeE{Thus} \changeE{thus} the derivative price is given by:
\begin{equation}
\begin{aligned}
	    V_{T_{k-1}}\left(X_{T_{k-1}}, I_{T_{k-1}}\right)= \\ 
	     \mathbb{E}_{T_{k-1}}\left[D\left(T_{k-1},T_{k}\right) V_{T_{k}}\left(X_{T_{k}}, I_{T_{k}}\left(\alpha_{T_{k-1}}\right)\right) \mid X_{T_{k-1}}, I_{T_{k-1}}\right] \; ,
\end{aligned}
\label{eq:recursion2}\end{equation}
while the iteration starts from maturity date where the boundary condition is set equal to the payoff function:
\begin{equation}
    V_{T_m} = \Phi\left(I_{T_m}\right) \; .
\end{equation}
